---
title: "Test"
author: "Kristin Braziunas"
date: "June 23, 2016"
output: html_document
---

```{r load-libraries }

library(raster)
library(rgdal)
library(neonAOP)
library(dplyr)
library(rhdf5)
library(rgeos)
library(ggplot2)

```

```{r do-some-test-plots }

setwd("~/Documents/data/NEONDI-2016/NEON_group_final/")
chm <- raster("../NEONdata/D17-California/SOAP/2013/lidar/SOAP_lidarCHM.tif")
insitu <- read.csv("../NEONdata/D17-California/SOAP/2013/insitu/veg-structure/D17_2013_SOAP_vegStr.csv")



plot(chm)
plot(stem_map, add=TRUE)
plot(centroids, add=TRUE, col="blue")

stem_map <- readOGR("../NEONdata/D17-California/SOAP/2013/insitu/veg-structure",
                    "soap_stems")



centroids <- readOGR("../NEONdata/D17-California/SOAP/vector_data",
                    "SOAP_centroids")

?plot

insitu.sub <- subset(insitu, easting < 298000 & northing > 4100400)
str(insitu)
str(insitu.sub)
plot(northing~easting, insitu.sub)

unique(insitu.sub$scientificname)
unique(insitu.sub$taxonid)

insitu.sub$taxonid <- gsub("CAIN3","CEIN3", insitu.sub$taxonid)
length(unique(insitu.sub$taxonid))
unique(insitu.sub$taxonid)

stem_map$taxonid <- gsub("CAIN3","CEIN3", stem_map$taxonid)


length(unique(stem_map$taxonid))
length(unique(stem_map$scientific))

?gsub

```

## Using Leah Wasser's github code to try to subset AOP HSI data

```{r subset-hsi }

## SOAP Clip
# the name of the site
site <- "SOAP"
domain <- "D17"
fullDomain <- "D17-California"
level <- "L1"
dataType <- "Spectrometer"
level <- paste0(site,"_L1")
year <- "2013"
productType <- paste0(site,"_", dataType)
dataProduct <- "Reflectance"


drivePath <- "Volumes"
driveName <- "AOP-NEON1-4"

dataDir <- file.path(drivePath, driveName,
                      domain,
                      site, year, level, productType, dataProduct)
dataDir <- paste0("/", dataDir)
# get a list of all files in the dir
h5.files <- list.files(dataDir, pattern = '\\.h5$', full.names = TRUE)

#### Import shapefile ####
# import shapefile
clipFilePath <- file.path("../NEONData", fullDomain, site, "vector_data")
clipFile <- paste0(site,"_crop")
clip.polygon <- readOGR(clipFilePath, clipFile)

#####
## functions
## Check Extent Function ####
# this function below checks to see if a raster falls within a spatial extent
# inputs: raster file to check, clipShp (spatial )
checkExtent <- function(aRaster, clipShp){
  # create polygon extent assign CRS to extent 
  h5.extent.sp <- as(h5Extent, "SpatialPolygons")
  # note this is ASSUMING both the extent and the h5 file are in the same CRS
  crs(rasterExtPoly) <-  crs(clip.polygon)

  # check to see if the polygons overlap
  # return a boolean (1= the raster contains pixels within the extent, 0 it doesn't)
  return(gIntersects(h5.extent.sp, clip.polygon))
}
# checkExtent("/Volumes/AOP-NEON1-4/D17/SOAP/2013/SOAP_L1/SOAP_Spectrometer/Reflectance/NIS1_20130615_165533_atmcor.h5")
# h5.files
# initalize counter and list object
recordRaster <- NA
i <- 0

# this loop is repeated below and can probably go away
# the loop below returns a LIST of the files that have overlapping extent
for(afile in h5.files){
  # get extent of h5 file
  h5Extent <- create_extent(afile)
  # turn into polygon extent object
  h5.poly <- as(h5Extent, "SpatialPolygons")
  # this is assuming both are in the same CRS!
  crs(h5.poly) <-  crs(clip.polygon)
  
  # check to see if the polygons overlap
  if(gIntersects(h5.poly, clip.polygon)){
    i <- i+1
    recordRaster[i] <- afile
  } else {
    print("not in")
  }
}

recordRaster

```

## Now that I've got Leah's code working, I'm going to create smaller extents based on our stem locations and see which ones have the fewest number of hyperspectral flight lines associated with them.

```{r create-plot-extents }

# first, I have to identify the boundaries of the plots where the stem locations
# are present, since stem locations do not totally match up with centroids

plot(stem_map)

# i'm extracting the northing and easting max and min and 
# adding or subtracting 5 as a buffer
stem_map.extent <- stem_map@data %>% 
  group_by(plotid) %>%
  summarise(northing.max = max(northing) + 5,
            northing.min = min(northing) - 5,
            easting.max = max(easting) + 5,
            easting.min = min(easting) - 5)

names(stem_map.extent) <- c("plotid","yPlus","yMinus","xPlus","xMinus")

yPlus <- stem_map.extent$northing.max
yMinus <- stem_map.extent$northing.min
xPlus <- stem_map.extent$easting.max
xMinus <- stem_map.extent$easting.min

# copying code from group uncertainty

square <- cbind(xMinus, yPlus, 
                xPlus, yPlus, 
                xPlus, yMinus, 
                xMinus, yMinus, 
                xMinus, yPlus,
                xMinus, yPlus)

ID <- stem_map.extent$plotid

```


## Create spatial polygons using the coordinates

```{r create-spatial-polygons }

# Create a function to do this
polys <- SpatialPolygons(mapply(function(poly, id) {
  xy <- matrix(poly, ncol=2, byrow=TRUE)  # take a list and create a matrix
  Polygons(list(Polygon(xy)), ID=id)
}, split(square, row(square)), ID),proj4string=CRS(as.character("+proj=utm +zone=11 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0")))

```

## Create shapefile

This is an important step to extract the data.

```{r create-shapefile }

polys.df <- SpatialPolygonsDataFrame(polys, data.frame(id=ID, row.names=ID))

```

## Plot this with our CHM

```{r plot-square-buffers }

plot(chm)
plot(polys.df, add=TRUE)

polys.df
clip.polygon

```

## Apply Leah's function with my new shapefiles

```{r match-plots-with-hsi }


find_intersect_h5 <- function(h5.files, clip.polygon){
  recordRaster <- NA
  i <- 0
  # the loop below returns a LIST of the files that have overlapping extent
  for(afile in h5.files){
    # get extent of h5 file
    h5Extent <- create_extent(afile)
    # turn into polygon extent object
    h5.poly <- as(h5Extent, "SpatialPolygons")
    # this is assuming both are in the same CRS!
    crs(h5.poly) <-  crs(clip.polygon)
    
    # check to see if the polygons overlap
    if(gIntersects(h5.poly, clip.polygon)){
      i <- i+1
      recordRaster[i] <- afile
    } else {
      print("not in")
    }
  } 
  return(recordRaster)
}

## Loop through all of the H5 files and return a list of what's "in"
intersect_files <- find_intersect_h5(h5.files, 
clip.polygon)

################### Next -- see if you can loop through polygons ####

# for this to work the shapefile has to have an "Id" field with numbers 1-x
soap.plots <- polys.df

# clip.file <- soap.plots[soap.plots$Id == 1,]
final.files <- vector("list", length(soap.plots))

# make copy of names
soap.plots$name <- soap.plots$id

# change id to numeric
soap.plots$id <- as.numeric(soap.plots$id)

# This for loop generates a list of flightlines that intersect each polygon in a 
# shapefile. Note that the spatial object needs an Id field that is numbered 1-n
for(i in 1:length(soap.plots)){
  clip.file <- soap.plots[soap.plots$id == i,]
  final.files[[i]] <- find_intersect_h5(h5.files, 
                                 clip.file)
  }


# this will separate mutiple polygons into individuals
first.box <- soap.plots[soap.plots$id == 1,]
first.box

second.box <- soap.plots[soap.plots$id == 2,]
second.box

first.box <- soap.plots[soap.plots$id == 1,]
first.box


# take a look at the output
str(final.files)
soap.plots@data


```

## I'm copying some more code from Leah to get the extents of each of the flightlines

```{r export-extents-hsi }

################ Write Extent Shapefiles Function ########################

# Inputs:
# f: a path to an h5 file that you'd like an extent for.
# shpDir: path to the output directory where you want to store the data
# projf4Str: the proj4 formated string of the CRS that the H5 file is in.
# NOTE: proj4 NEEDS to be in the same proj as your h5 file
write_shapefile_bound <- function(f, shpDir, proj4Str){
  # create shapefileName
  # output
  h5.extent <- create_extent(f)
  # create polygon extent assign CRS to extent 
  h5.extent.sp <- as(h5.extent, "SpatialPolygons")
  # create data.frame, add the name of the file to the shapefile
  sp.df <- data.frame(id=basename(f))
  sp.obj <- SpatialPolygonsDataFrame(h5.extent.sp, sp.df)
  # assign CRS
  crs(sp.obj) <- CRS(proj4Str)
  # create shapefile output name
  outName <- gsub(pattern = ".h5",
                  x = basename(f),
                  replacement = "")
  writeOGR(sp.obj, 
           shpDir, #path to export to
           outName,
           driver="ESRI Shapefile",
           overwrite_layer = TRUE)
}

##################### Run Export Polygon Boundary for Each Flightline ##############

# export extent polygon for all flightlines
proj4Str <- "+proj=utm +zone=11 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs"
shpDir <- paste0("exports/", site, "_flightLines")

sapply(h5.files, write_shapefile_bound,
       proj4Str = proj4Str,
       shpDir = shpDir)

#################### End Export Polygon Boundary for Each Flightline ###########



```

## I'm going to choose a couple flightlines to load the extents for

```{r load-hsi-shapefiles }

plot(chm)
plot(polys.df, add=TRUE)

flight1 <- readOGR("exports/SOAP_flightLines","NIS1_20130612_104000_atmcor")
plot(flight1, add=TRUE)
# there are 4 plots close to the center

flight2 <- readOGR("exports/SOAP_flightLines","NIS1_20130612_104651_atmcor")
plot(flight2, add=TRUE)
# there are 4 plots close to the center, so choose these

polys.df
plot(second.box, add=TRUE)

soap.plots@polygons[[1]]@Polygons[[1]]@coords

```

## Let's try using second.box to extract HSI data from flight2

```{r extract-hsi }

# choose the plots that intersect with flight 2 for extracting HSI
flight2.plots <- intersect(soap.plots, flight2)
flight2.plots

# define the CRS definition by EPSG code
epsg <- 32611


# define the file you want to work with
f <- paste0(dataDir, "/NIS1_20130612_104651_atmcor.h5")

# define clip.extents
clip.extent <- flight2.plots

# calculate extent of H5 file
h5.ext <- create_extent(f)
h5.ext

## class       : Extent 
## xmin        : 325963 
## xmax        : 326507 
## ymin        : 4102904 
## ymax        : 4103482

# turn the H5 extent into a polygon to check overlap
h5.ext.poly <- as(extent(h5.ext), 
                  "SpatialPolygons")

crs(h5.ext.poly) <- crs(clip.extent)

# test to see that the extents overlap
gIntersects(h5.ext.poly, 
            clip.extent)

## [1] TRUE

# Use the clip extent to create the index extent that can be used to slice out data from the 
# H5 file
# xmin.index, xmax.index, ymin.index, ymax.index
# all units will be rounded which means the pixel must occupy a majority (.5 or greater)
# within the clipping extent
clip.extent[clip.extent$id.1 == i,]

index.bounds <- vector("list", length(clip.extent))

for(i in 1:length(clip.extent)) {
  index.bounds[[i]] <- calculate_index_extent(extent(clip.extent[clip.extent$id.1 == i,]),
								h5.ext)
}
index.bounds

index.bounds <- calculate_index_extent(extent(clip.extent),
								h5.ext)
index.bounds
write.csv(index.bounds,"index_bounds.csv")

## [1]  39 127  21  92

# # open a band that is subsetted using the clipping extent
# # if you set subsetData to true, then provide the dimensions that you wish to slice out
# for(i in length(index.bounds)) {
  b58_clipped <- open_band(fileName=f,
	  							bandNum=58,
		  						epsg=32611,
			  					subsetData = TRUE,
				  				dims=index.bounds)
# }
# plot(chm)
# # plot clipped bands
# plot(flight2.plots, add=TRUE)
# plot(b58_clipped,
#      main="Band 58 Clipped", add=TRUE, col="red")
# 
# plot(b58_clipped,
#      main="Band 58 Clipped")
# 
# b58_clipped

```

```{r extract-hsi-bands }

# create  alist of the bands
bands <- c(300:400)

# clip out raster
rgbRast.clip <- create_stack(file=f,
            bands=bands,
            epsg=epsg,
            subset=TRUE,
            dims=index.bounds)


plotRGB(rgbRast.clip,
        stretch="lin")

```

## Get index bounds for the next set of plots

```{r flight1-plots }

# choose the plots that intersect with flight 1 for extracting HSI
flight1.plots <- intersect(soap.plots, flight1)
flight1.plots

# plot it
plot(chm)
plot(flight1.plots.sub, add=TRUE)

unique(flight1.plots$id.1)
unique(flight2.plots$id.1)

flight1.plots.sub <- subset(flight1.plots, flight1.plots$id.1 == 4 |
                              flight1.plots$id.1 == 6 | flight1.plots$id.1 == 8 |
                              flight1.plots$id.1 == 12)
str(flight1.plots.sub)
# define the CRS definition by EPSG code
epsg <- 32611


# define the file you want to work with
f <- paste0(dataDir, "/NIS1_20130612_104000_atmcor.h5")

# define clip.extents
clip.extent <- flight1.plots.sub

# calculate extent of H5 file
h5.ext <- create_extent(f)
h5.ext

## class       : Extent 
## xmin        : 325963 
## xmax        : 326507 
## ymin        : 4102904 
## ymax        : 4103482

# turn the H5 extent into a polygon to check overlap
h5.ext.poly <- as(extent(h5.ext), 
                  "SpatialPolygons")

crs(h5.ext.poly) <- crs(clip.extent)

# test to see that the extents overlap
gIntersects(h5.ext.poly, 
            clip.extent)

## [1] TRUE

# Use the clip extent to create the index extent that can be used to slice out data from the 
# H5 file
# xmin.index, xmax.index, ymin.index, ymax.index
# all units will be rounded which means the pixel must occupy a majority (.5 or greater)
# within the clipping extent
clip.extent[clip.extent$id.1 == i,]

index.bounds <- vector("list", length(clip.extent))

for(i in 1:length(clip.extent)) {
  index.bounds[[i]] <- calculate_index_extent(extent(clip.extent[clip.extent$id.1 == i,]),
								h5.ext)
}
index.bounds

index.bounds <- calculate_index_extent(extent(clip.extent),
								h5.ext)
index.bounds
write.csv(index.bounds,"index_bounds2.csv")

plot(chm)
plot(flight1.plots.sub, add=TRUE)
plot(b58_clipped, add=TRUE, col="red")

?group_by


```

## Let's read in some wavelengths

```{r read-wavelengths }

# read in the wavelength information from the HDF5 file
wavelengths <- h5read(f, "wavelength")
head(wavelengths)

##         [,1]
## [1,] 0.38227
## [2,] 0.38728
## [3,] 0.39229
## [4,] 0.39730
## [5,] 0.40231
## [6,] 0.40732

# NOTE: this currently doesn't work properly if the file is rotated
h5.ext <- create_extent(f)

# calculate the index subset dims to extract data from the H5 file
subset.dims <- calculate_index_extent(clip.extent, 
                    h5.ext, 
                    xscale = 1, yscale = 1)


# turn the H5 extent into a polygon to check overlap
h5.ext.poly <- as(extent(h5.ext),
                "SpatialPolygons")

# assign crs to new polygon
crs(h5.ext.poly) <- CRS("+proj=utm +zone=11 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0")

# ensure the two extents overlap
gIntersects(h5.ext.poly, 
            clip.extent)

## [1] TRUE

# finally determine the subset to extract from the h5 file
index.bounds <- calculate_index_extent(extent(clip.extent), 
                h5.ext)

# open a band
a.raster <- open_band(f, 
                      56, 
                      epsg)

# grab the average reflectance value for a band
refl <- extract_av_refl(a.raster, 
                        aFun = mean)

refl

## [1] 0.1037593
# grab all bands
bands <- c(1:192,214:282,316:403)

# get stack
all.bands.stack <- create_stack(f, 
                         bands, 
                         epsg,
                         subset=TRUE,
                         dims=index.bounds)

plot(chm)
plot(all.bands.stack[[1]], add=TRUE, col="red")

# get spectra for each band
spectra <- extract_av_refl(all.bands.stack, 
                           aFun = mean)
spectra <- as.data.frame(spectra)

# read in the wavelength information from the HDF5 file
wavelengths<- h5read(f, "wavelength")

# convert wavelength to nanometers (nm)
wavelengths <- wavelengths * 1000

spectra$wavelength <- wavelengths[bands]

wavelengths


# plot spectra
qplot(x=spectra$wavelength,
      y=spectra$spectra,
      xlab="Wavelength (nm)",
      ylab="Reflectance",
      main="Spectra for all pixels",
      ylim = c(0, .35))

```

