---
title: "Test"
author: "Kristin Braziunas"
date: "June 23, 2016"
output: html_document
---

```{r load-libraries, echo=FALSE }

library(raster)
library(rgdal)
library(neonAOP)
library(dplyr)
library(rhdf5)
library(rgeos)
library(ggplot2)

```

## Load canopy height model

```{r load-chm }

chm <- raster("../NEONdata/D17-California/SOAP/2013/lidar/SOAP_lidarCHM.tif")

```


## Identify plot boundaries

We wanted to match up our in situ data with the hyperspectral data so that we could subset a hyperspectral flight line. As a first step, we identified plot boundaries based on the stem locations in the in situ data.

## First, we load the in situ data as a shapefile

```{r load-insitu-data }

stem.map <- readOGR("../NEONdata/D17-California/SOAP/2013/insitu/veg-structure",
                    "soap_stems")

# look at a plot
plot(chm)
plot(stem.map, add=TRUE)

```

## Use stem locations to create plot boundaries

```{r create-plot-boundaries }

# group stems by plotid, record the max and min northing and easting values
# this will be used later to create a shapefile for plot boundaries
stem.map.extent <- stem.map@data %>% 
  group_by(plotid) %>%
  summarise(northing.max = max(northing) + 5,
            northing.min = min(northing) - 5,
            easting.max = max(easting) + 5,
            easting.min = min(easting) - 5)

# assign new variables for use with previously created code
yPlus <- stem.map.extent$northing.max
yMinus <- stem.map.extent$northing.min
xPlus <- stem.map.extent$easting.max
xMinus <- stem.map.extent$easting.min

# code from NEON tutorial on creating square plot extents
square <- cbind(xMinus, yPlus, 
                xPlus, yPlus, 
                xPlus, yMinus, 
                xMinus, yMinus, 
                xMinus, yPlus)

ID <- stem.map.extent$plotid

```

## Create spatial polygons using the coordinates

```{r create-spatial-polygons }

# Create a function to do this
polys <- SpatialPolygons(mapply(function(poly, id) {
  xy <- matrix(poly, ncol=2, byrow=TRUE)  # take a list and create a matrix
  Polygons(list(Polygon(xy)), ID=id)
}, split(square, row(square)), ID),proj4string=CRS(as.character("+proj=utm +zone=11 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0")))

```

## Create shapefile

```{r create-shapefile }

polys.df <- SpatialPolygonsDataFrame(polys, data.frame(id=ID, row.names=ID))

```

## Plot this with our CHM

```{r plot-square-buffers }

plot(chm)
plot(polys.df, add=TRUE)

```

## Look at all the hyperspectral flightlines

We used Leah's code to look through all the hyperspectral flightlines. I'm not going to rehash it all here, but we decided to narrow down to one flightline that covered 4 plots.

We also used Leah's code to get extents for all flightlines and saved this on our local computer.

## Set data directory to access hyperspectral flightline from hard drive

```{r set-data-directory }

## SOAP Clip
# the name of the site
site <- "SOAP"
domain <- "D17"
fullDomain <- "D17-California"
level <- "L1"
dataType <- "Spectrometer"
level <- paste0(site,"_L1")
year <- "2013"
productType <- paste0(site,"_", dataType)
dataProduct <- "Reflectance"

drivePath <- "Volumes"
driveName <- "AOP-NEON1-4"

dataDir <- file.path(drivePath, driveName,
                      domain,
                      site, year, level, productType, dataProduct)
dataDir <- paste0("/", dataDir)

```

## Import flightline

The right boundary of the flightline appears on the plot below

```{r import-flightline }

flight1 <- readOGR("exports/SOAP_flightLines","NIS1_20130612_104651_atmcor")

# look at this with our plots
plot(chm)
plot(polys.df, add=TRUE)
plot(flight1, add=TRUE)

```

## Identify plots within flightline

Note that 4 plots are close to the center of the flightline. We will subset for those 4 plots.

```{r subset-plot-shapefiles }

# choose the plots that intersect with flight 1 for extracting HSI
flight1.plots <- intersect(polys.df, flight1)
flight1.plots

# check this subset
plot(chm)
plot(flight1.plots, add=TRUE)

```

## Boundary for hyperspectral subset

Now we create a boundary that includes all 4 plots to subset the hyperspectral data.

```{r overall-plot-boundary }

# thanks for the code, leah!

# define the CRS definition by EPSG code
epsg <- 32611

# define the file you want to work with
# this is the hyperspectral flightline from the hard drive
f <- paste0(dataDir, "/NIS1_20130612_104651_atmcor.h5")

# define clip.extents
clip.extent <- flight1.plots

# calculate extent of H5 file
h5.ext <- create_extent(f)
h5.ext

# turn the H5 extent into a polygon to check overlap
h5.ext.poly <- as(extent(h5.ext), 
                  "SpatialPolygons")

crs(h5.ext.poly) <- crs(clip.extent)

# test to see that the extents overlap
gIntersects(h5.ext.poly, 
            clip.extent)

# Use the clip extent to create the index extent that can be used to slice out data from the 
# H5 file
# xmin.index, xmax.index, ymin.index, ymax.index
# all units will be rounded which means the pixel must occupy a majority (.5 or greater)
# within the clipping extent

index.bounds <- vector("list", length(clip.extent))

index.bounds <- calculate_index_extent(extent(clip.extent),
								h5.ext)
index.bounds

# this is what i wrote to a csv!

```
