
---
title: "NEON_group_final"
author: "Megan Cattau, Kristin Braziunas"
date: "June 23, 2016"
output: html_document
---

# How do forest charcteristics vary as a function of disturbance history in SOAP, CA?

## This is the random forest classification that will be used as a metric of forest characteristics

```{r load_packages}
# Check working directory
getwd()

# Load our packages
library(raster)
library(rgdal)
library(ggplot2)
library(dplyr)
library(sp)
library(neonAOP)
library(rhdf5)
# install.packages("randomForest")
library(randomForest)

setwd("C:/Users/stellac/Box Sync/Work/neonwksp/data/NEONDI-2016/NEON_group_final/Scripts")
```

### Load data
Load LiDAR data - CHM, Slope, and Aspect
```{r load_LiDAR_data}
# Load LiDAR CHM raster
soap_chm<-raster("../../NEONdata/D17-California/SOAP/2013/lidar/SOAP_lidarCHM.tif")
# look at it
hist(soap_chm)
summary(soap_chm)
# Load LiDAR Slope raster
soap_slope<-raster("../../NEONdata/D17-California/SOAP/2013/lidar/SOAP_lidarSlope.tif")
# look at it
hist(soap_slope)
summary(soap_slope)
# Load LiDAR Aspect raster
soap_aspect<-raster("../../NEONdata/D17-California/SOAP/2013/lidar/SOAP_lidarAspect.tif")
# look at it
hist(soap_aspect)
summary(soap_aspect)
# LiDAR data stack
LiDAR.data<-brick(soap_chm,soap_slope,soap_aspect)
```

Load HI data
```{r import_hI}
# Import the HI data
# In the absence of reflectance, we've got indices
soap_HI_NDVI<-raster("../../NEONdata/D17-California/SOAP/2013/spectrometer/veg_index/SOAP_NDVI.tif")
plot(soap_HI_NDVI)
summary(soap_HI_NDVI)
soap_HI_SAVI<-raster("../../NEONdata/D17-California/SOAP/2013/spectrometer/veg_index/SOAP_SAVI.tif")
plot(soap_HI_SAVI)
summary(soap_HI_SAVI)
soap_HI_ARVI<-raster("../../NEONdata/D17-California/SOAP/2013/spectrometer/veg_index/SOAP_ARVI.tif")
plot(soap_HI_ARVI)
summary(soap_HI_ARVI)
soap_HI_EVI<-raster("../../NEONdata/D17-California/SOAP/2013/spectrometer/veg_index/SOAP_EVI.tif")
plot(soap_HI_EVI)
summary(soap_HI_EVI)
soap_HI_NDLI<-raster("../../NEONdata/D17-California/SOAP/2013/spectrometer/veg_index/SOAP_NDLI.tif")
plot(soap_HI_NDLI)
summary(soap_HI_NDLI)
soap_HI_NDNI<-raster("../../NEONdata/D17-California/SOAP/2013/spectrometer/veg_index/SOAP_NDNI.tif")
plot(soap_HI_NDNI)
summary(soap_HI_NDNI)
soap_HI_PRI<-raster("../../NEONdata/D17-California/SOAP/2013/spectrometer/veg_index/SOAP_PRI.tif")
plot(soap_HI_PRI)
summary(soap_HI_PRI)

# HI data stack
HI.data<-brick(soap_HI_NDVI,soap_HI_SAVI, soap_HI_ARVI, soap_HI_EVI,soap_HI_NDLI, soap_HI_NDNI, soap_HI_PRI)
```

# Load insitu measurements
```{r load_field_measurements}
# Load insitu veg data
# soap_insitu1<-read.csv("../../NEONdata/D17-California/SOAP/2013/insitu/veg-structure/D17_2013_SOAP_vegStr.csv", stringsAsFactors = FALSE)
# we don't need the above because the same info is in the below

soap_insitu<-readOGR("../../NEONdata/D17-California/SOAP/2013/insitu/veg-structure", "soap_stems")
names(soap_insitu)
str(soap_insitu)

# How many species are there at this site?
length(unique(soap_insitu$taxonid))
length(unique(soap_insitu$scientific))

# The data says there are 17 taxonids and 16 spp, so we needed to fix the erroneous taxonid

soap_insitu$taxonid<-gsub("CAIN3", "CEIN3", soap_insitu$taxonid)
# It's fixed! Now there are 16 taxonids and 16 scientific names
```


## Braziunas edits start here. I'm going to start by importing the index boundaries for the two areas, each with 4 plots, where we are going to pull out hyperspectral data.

```{r import-index-boundaries }

# first import the boundaries
index.bounds.flight1 <- read.csv("../index_bounds.csv", sep=",")[,2]
index.bounds.flight2 <- read.csv("../index_bounds2.csv", sep=",")[,2]

```

## Import flightpaths previously identified

```{r import-hsi-flightpaths }

flight1 <- "/Volumes/AOP-NEON1-4/D17/SOAP/2013/SOAP_L1/SOAP_Spectrometer/Reflectance/NIS1_20130612_104651_atmcor.h5"

flight2 <- "/Volumes/AOP-NEON1-4/D17/SOAP/2013/SOAP_L1/SOAP_Spectrometer/Reflectance/NIS1_20130612_104000_atmcor.h5"

```

## Extract bands from flightpaths

```{r extract-bands }

# thanks to Leah, we know which bands are noisy
# so only importing bands that are not noisy

# grab all bands
bands <- c(1:192,214:282,316:403)

# set epsg
epsg <- 32611

# get stack
all.bands.stack.flight1 <- create_stack(flight1, 
                         bands, 
                         epsg,
                         subset=TRUE,
                         dims=index.bounds.flight1)

# get stack
all.bands.stack.flight2 <- create_stack(flight2, 
                         bands, 
                         epsg,
                         subset=TRUE,
                         dims=index.bounds.flight2)

# check via plotting to make sure we got the right areas
plot(soap_chm)
plot(all.bands.stack.flight1[[1]], add=TRUE, col="red")
plot(all.bands.stack.flight2[[1]], add=TRUE, col="blue")

# also take a look at the wavelength plots

# get spectra for each band
spectra.flight1 <- extract_av_refl(all.bands.stack.flight1, 
                           aFun = mean)
spectra.flight1 <- as.data.frame(spectra.flight1)

# read in the wavelength information from the HDF5 file
wavelengths<- h5read(flight1, "wavelength")

# convert wavelength to nanometers (nm)
wavelengths <- wavelengths * 1000

spectra.flight1$wavelength <- wavelengths[bands]

# plot spectra
qplot(x=spectra.flight1$wavelength,
      y=spectra.flight1$spectra.flight1,
      xlab="Wavelength (nm)",
      ylab="Reflectance",
      main="Spectra for all pixels\nFlight1",
      ylim = c(0, .35))

## now flight 2
# get spectra for each band
spectra.flight2 <- extract_av_refl(all.bands.stack.flight2, 
                           aFun = mean)
spectra.flight2 <- as.data.frame(spectra.flight2)

# read in the wavelength information from the HDF5 file
wavelengths<- h5read(flight2, "wavelength")

# convert wavelength to nanometers (nm)
wavelengths <- wavelengths * 1000

spectra.flight2$wavelength <- wavelengths[bands]

wavelengths

# plot spectra
qplot(x=spectra.flight2$wavelength,
      y=spectra.flight2$spectra.flight2,
      xlab="Wavelength (nm)",
      ylab="Reflectance",
      main="Spectra for all pixels\nFlight 2",
      ylim = c(0, .35))

```
### Braziunas ends here


