---
title: ""
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
---

```{r knitr_init,echo=FALSE, cache=FALSE, background= "blue"}
library(knitr)
library(rmdformats)

## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=FALSE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

---
title: "NEON_group_final"
author: "Megan Cattau, Kristin Braziunas, Stella Cousins, and Allie Weill"
date: "June 23, 2016"
output: readthedown 
---

# How do forest charcteristics vary with respect to disturbance history at Soaproot Saddle?

## _Using random forests to classify remotely sensed forest characteristics_

```{r load_packages, echo = FALSE}
## Check working directory
#getwd()

# Load our packages
library(raster)
library(rgdal)
library(ggplot2)
library(ggthemes)
library(dplyr)
library(sp)
library(neonAOP)
library(rhdf5)
# install.packages("randomForest")
library(randomForest)

setwd("C:/Users/stellac/Box Sync/Work/neonwksp/data/NEONDI-2016/NEON_group_final/Scripts")
```

### 1. Load data
  Load LiDAR data Canopy Height Slope and Aspect
```{r load_LiDAR_data}
# Load LiDAR CHM raster
soap_chm<-raster("../../NEONdata/D17-California/SOAP/2013/lidar/SOAP_lidarCHM.tif")
# look at it
#summary(soap_chm)
# Load LiDAR Slope raster
soap_slope <-raster("../../NEONdata/D17-California/SOAP/2013/lidar/SOAP_lidarSlope.tif")

# Load LiDAR Aspect raster
soap_aspect <-raster("../../NEONdata/D17-California/SOAP/2013/lidar/SOAP_lidarAspect.tif")
# look at it

par(mfrow=c(1,3))
hist(soap_aspect, main = "Aspect", col = "cornflower blue")
hist(soap_chm,main = "Canopy Height", col="springgreen")
hist(soap_slope, main = "Slope", col = "purple")
par(mfrow = c(1,1))
#summary(soap_aspect)
# LiDAR data stack
LiDAR.data<-brick(soap_chm,soap_slope,soap_aspect)
```

###Load HI data
Get hyperspectral indices NDVI, SAVI, ARVI, EVI, NLDI, NDNI, and PRI for the site.
We don't need to see that.

```{r import_hI, echo = FALSE}
# Import the HI data
# In the absence of reflectance, we've got indices
soap_HI_NDVI<-raster("../../NEONdata/D17-California/SOAP/2013/spectrometer/veg_index/SOAP_NDVI.tif")
#plot(soap_HI_NDVI)
#summary(soap_HI_NDVI)
soap_HI_SAVI<-raster("../../NEONdata/D17-California/SOAP/2013/spectrometer/veg_index/SOAP_SAVI.tif")
#plot(soap_HI_SAVI)
#summary(soap_HI_SAVI)
soap_HI_ARVI<-raster("../../NEONdata/D17-California/SOAP/2013/spectrometer/veg_index/SOAP_ARVI.tif")
#plot(soap_HI_ARVI)
#summary(soap_HI_ARVI)
soap_HI_EVI<-raster("../../NEONdata/D17-California/SOAP/2013/spectrometer/veg_index/SOAP_EVI.tif")
#plot(soap_HI_EVI)
#summary(soap_HI_EVI)
soap_HI_NDLI<-raster("../../NEONdata/D17-California/SOAP/2013/spectrometer/veg_index/SOAP_NDLI.tif")
#plot(soap_HI_NDLI)
#summary(soap_HI_NDLI)
soap_HI_NDNI<-raster("../../NEONdata/D17-California/SOAP/2013/spectrometer/veg_index/SOAP_NDNI.tif")
#plot(soap_HI_NDNI)
#summary(soap_HI_NDNI)
soap_HI_PRI<-raster("../../NEONdata/D17-California/SOAP/2013/spectrometer/veg_index/SOAP_PRI.tif")
#plot(soap_HI_PRI)
#summary(soap_HI_PRI)
```

### Create brick of vegetation indices
```{r make-raster-brick}
## HI data stack
HI.data<-brick(soap_HI_NDVI,soap_HI_SAVI, soap_HI_ARVI, soap_HI_EVI,soap_HI_NDLI, soap_HI_NDNI, soap_HI_PRI)
```

### Load Field Measurements
```{r load_field_measurements}
# Load insitu veg data
# soap_insitu1<-read.csv("../../NEONdata/D17-California/SOAP/2013/insitu/veg-structure/D17_2013_SOAP_vegStr.csv", stringsAsFactors = FALSE)
# we don't need the above because the same info is in the below

soap_insitu<-readOGR("../../NEONdata/D17-California/SOAP/2013/insitu/veg-structure", "soap_stems")
#names(soap_insitu)
#str(soap_insitu)

# The data says there are 17 taxonids and 16 spp, so we needed to fix the erroneous taxonid

soap_insitu$taxonid<-gsub("CAIN3", "CEIN3", soap_insitu$taxonid)
# It's fixed! Now there are 16 taxonids and 16 scientific names
```

## Import index boundaries
We extracted the flight boundaries using a special sauce
```{r import-index-boundaries, echo= TRUE }
# first import the boundaries
#KB wants to add more elaboration here to elaborate the index bounds
index.bounds.flight1 <- read.csv("../index_bounds.csv", sep=",")[,2]

```

## Import flightpaths previously identified

```{r import-hsi-flightpaths }

flight1 <- "D:/D17/SOAP/2013/SOAP_L1/SOAP_Spectrometer/Reflectance/NIS1_20130612_104651_atmcor.h5"
```

## Extract bands from flightpaths
This flightpath brought to you by Leah Wasser. Thanks Leah!
```{r extract-bands }

# thanks to Leah, we know which bands are noisy
# so only importing bands that are not noisy

# grab all bands
bands <- c(1:192,214:282,316:403)
bands_rgb <- c( 58,34,19)
# set epsg
epsg <- 32611

# get stack
all.bands.stack.flight1 <- create_stack(flight1, 
                         bands, 
                         epsg,
                         subset=TRUE,
                         dims=index.bounds.flight1)

rgb.bands.stack.flight1 <- create_stack(flight1, 
                         bands_rgb, 
                         epsg,
                         subset=TRUE,
                         dims=index.bounds.flight1)

# check via plotting to make sure we got the right areas

plot(soap_chm,xlim = c(296800,298000))
#plot(soap_)
plot(extent(all.bands.stack.flight1),add=T, col = "cornflower blue")
plotRGB(rgb.bands.stack.flight1,stretch ="lin",add=T)

# also take a look at the wavelength plots

# get spectra for each band
spectra.flight1 <- extract_av_refl(all.bands.stack.flight1, 
                           aFun = mean)
spectra.flight1 <- as.data.frame(spectra.flight1)

# read in the wavelength information from the HDF5 file
wavelengths<- h5read(flight1, "wavelength")

# convert wavelength to nanometers (nm)
wavelengths <- wavelengths * 1000

spectra.flight1$wavelength <- wavelengths[bands]

# plot spectra
spectra_plot <- qplot(x=spectra.flight1$wavelength,
      y=spectra.flight1$spectra.flight1,
      xlab="Wavelength (nm)",
      ylab="Reflectance",
      main="Spectra for all pixels\nSoaproot Saddle Flightpath 1",
      ylim = c(0, .35), colour=spectra.flight1$wavelength)
spectra_plot + theme_few()

```

###The end. 

