---
title: "NEON_group_final"
author: "Megan Cattau, Kristin Braziunas"
date: "June 23, 2016"
output: html_document
---

# How do forest charcteristics vary as a function of disturbance history in SOAP, CA?

## This is the random forest classification that will be used as a metric of forest characteristics

```{r load_packages}
# Check working directory
getwd()

# Load our packages
library(raster)
library(rgdal)
library(ggplot2)
library(dplyr)
library(sp)
setwd("~/Documents/data/NEONDI-2016/NEON_group_final/Scripts/")
```

### Load data
Load LiDAR data - CHM, Slope, and Aspect
```{r load_LiDAR_data}
# Load LiDAR CHM raster
soap_chm<-raster("../../NEONdata/D17-California/SOAP/2013/lidar/SOAP_lidarCHM.tif")
# look at it
hist(soap_chm)

# Load LiDAR Slope raster
soap_slope<-raster("../../NEONdata/D17-California/SOAP/2013/lidar/SOAP_lidarSlope.tif")
# look at it
hist(soap_slope)

# Load LiDAR Aspect raster
soap_aspect<-raster("../../NEONdata/D17-California/SOAP/2013/lidar/SOAP_lidarAspect.tif")
# look at it
hist(soap_aspect)

# LiDAR data stack
LiDAR.data<-brick(soap_chm,soap_slope,soap_aspect)
```

Load HI data
```{r import_hI}
# Import the HI data
# In the absence of reflectance, we've got indices
soap_HI_NDVI<-raster("../../NEONdata/D17-California/SOAP/2013/spectrometer/veg_index/SOAP_NDVI.tif")
plot(soap_HI_NDVI)
summary(soap_HI_NDVI)
soap_HI_SAVI<-raster("../../NEONdata/D17-California/SOAP/2013/spectrometer/veg_index/SOAP_SAVI.tif")
plot(soap_HI_SAVI)
summary(soap_HI_SAVI)
soap_HI_ARVI<-raster("../../NEONdata/D17-California/SOAP/2013/spectrometer/veg_index/SOAP_ARVI.tif")
plot(soap_HI_ARVI)
summary(soap_HI_ARVI)
soap_HI_EVI<-raster("../../NEONdata/D17-California/SOAP/2013/spectrometer/veg_index/SOAP_EVI.tif")
plot(soap_HI_EVI)
summary(soap_HI_EVI)
soap_HI_NDLI<-raster("../../NEONdata/D17-California/SOAP/2013/spectrometer/veg_index/SOAP_NDLI.tif")
plot(soap_HI_NDLI)
summary(soap_HI_NDLI)
soap_HI_NDNI<-raster("../../NEONdata/D17-California/SOAP/2013/spectrometer/veg_index/SOAP_NDNI.tif")
plot(soap_HI_NDNI)
summary(soap_HI_NDNI)
soap_HI_PRI<-raster("../../NEONdata/D17-California/SOAP/2013/spectrometer/veg_index/SOAP_PRI.tif")
plot(soap_HI_PRI)
summary(soap_HI_PRI)

# HI data stack
HI.data<-brick(soap_HI_NDVI,soap_HI_SAVI, soap_HI_ARVI, soap_HI_EVI,soap_HI_NDLI, soap_HI_NDNI, soap_HI_PRI)
```

Put data together
```{r combine data}
# write a function to compare extents and crop layers if they are different
same_extent<-function(raster1, raster2) {
  if (extent(raster1)==extent(raster2)) {
    print("Rasters have same extent")
  } else {
    overlap<-raster::intersect(extent(raster1), extent(raster2))
    # crop both rasters
    # might be good to check which is bigger and compare
    print("Extents are different, Cropping data")
    raster1<-crop(raster1, overlap)
    raster2<-crop(raster2, overlap)
    # create a stack of the new rasters
  }
    raster.stack<-stack(raster1, raster2)
    return(raster.stack)
}


# check our data
all.data<-stack(HI.data, LiDAR.data)
all.data
```

# Make a df of the indices and examine which are correlated
```{r corr-variables}

# look at correlation bt variables
all.data.df<-as.data.frame(all.data)
cordf<-na.omit(all.data.df)
str(cordf)

# if more than 0.4, correlated, don't use some or put interaction'
coor.cordf<-round(cor(cordf),2)
#export as csv to variables.correlation
write.csv(coor.cordf,"../Outputs/var_cor_no_reflectance.csv")


### ADD REFLECTANCE!!
```

# Load insitu measurements
```{r load_field_measurements}
# Load insitu veg data
# soap_insitu1<-read.csv("../../NEONdata/D17-California/SOAP/2013/insitu/veg-structure/D17_2013_SOAP_vegStr.csv", stringsAsFactors = FALSE)
# we don't need the above because the same info is in the below

soap_insitu<-readOGR("../../NEONdata/D17-California/SOAP/2013/insitu/veg-structure", "soap_stems")
names(soap_insitu)
str(soap_insitu)

# How many species are there at this site?
length(unique(soap_insitu$taxonid))
length(unique(soap_insitu$scientific))

# The data says there are 17 taxonids and 16 spp, so we needed to fix the erroneous taxonid

soap_insitu$taxonid<-gsub("CAIN3", "CEIN3", soap_insitu$taxonid)
# It's fixed! Now there are 16 taxonids and 16 scientific names
```

Make a data cube
Sample HI and LiDAR data at stem points

Withhold 20 % of insitu for validataion

Random forest classification

Fin


