---
title: "NEON_group_final"
author: "Megan Cattau, Kristin Braziunas"
date: "June 23, 2016"
output: html_document
---

# How do forest charcteristics vary as a function of disturbance history in SOAP, CA?

## This is the random forest classification that will be used as a metric of forest characteristics

```{r load_packages}
# Check working directory
getwd()

# Load our packages
library(raster)
library(rgdal)
library(ggplot2)
library(dplyr)
library(sp)
# install.packages("randomForest")
library(randomForest)

setwd("~/Documents/data/NEONDI-2016/NEON_group_final/Scripts/")
```

### Load data
Load LiDAR data - CHM, Slope, and Aspect
```{r load_LiDAR_data}
# Load LiDAR CHM raster
soap_chm<-raster("../../NEONdata/D17-California/SOAP/2013/lidar/SOAP_lidarCHM.tif")
# look at it
hist(soap_chm)
summary(soap_chm)
# Load LiDAR Slope raster
soap_slope<-raster("../../NEONdata/D17-California/SOAP/2013/lidar/SOAP_lidarSlope.tif")
# look at it
hist(soap_slope)
summary(soap_slope)
# Load LiDAR Aspect raster
soap_aspect<-raster("../../NEONdata/D17-California/SOAP/2013/lidar/SOAP_lidarAspect.tif")
# look at it
hist(soap_aspect)
summary(soap_aspect)
# LiDAR data stack
LiDAR.data<-brick(soap_chm,soap_slope,soap_aspect)
```

Load HI data
```{r import_hI}
# Import the HI data
# In the absence of reflectance, we've got indices
soap_HI_NDVI<-raster("../../NEONdata/D17-California/SOAP/2013/spectrometer/veg_index/SOAP_NDVI.tif")
plot(soap_HI_NDVI)
summary(soap_HI_NDVI)
soap_HI_SAVI<-raster("../../NEONdata/D17-California/SOAP/2013/spectrometer/veg_index/SOAP_SAVI.tif")
plot(soap_HI_SAVI)
summary(soap_HI_SAVI)
soap_HI_ARVI<-raster("../../NEONdata/D17-California/SOAP/2013/spectrometer/veg_index/SOAP_ARVI.tif")
plot(soap_HI_ARVI)
summary(soap_HI_ARVI)
soap_HI_EVI<-raster("../../NEONdata/D17-California/SOAP/2013/spectrometer/veg_index/SOAP_EVI.tif")
plot(soap_HI_EVI)
summary(soap_HI_EVI)
soap_HI_NDLI<-raster("../../NEONdata/D17-California/SOAP/2013/spectrometer/veg_index/SOAP_NDLI.tif")
plot(soap_HI_NDLI)
summary(soap_HI_NDLI)
soap_HI_NDNI<-raster("../../NEONdata/D17-California/SOAP/2013/spectrometer/veg_index/SOAP_NDNI.tif")
plot(soap_HI_NDNI)
summary(soap_HI_NDNI)
soap_HI_PRI<-raster("../../NEONdata/D17-California/SOAP/2013/spectrometer/veg_index/SOAP_PRI.tif")
plot(soap_HI_PRI)
summary(soap_HI_PRI)

# HI data stack
HI.data<-brick(soap_HI_NDVI,soap_HI_SAVI, soap_HI_ARVI, soap_HI_EVI,soap_HI_NDLI, soap_HI_NDNI, soap_HI_PRI)
```

Put data together in a datacube
```{r combine data}
# write a function to compare extents and crop layers if they are different
same_extent<-function(raster1, raster2) {
  if (extent(raster1)==extent(raster2)) {
    print("Rasters have same extent")
  } else {
    overlap<-raster::intersect(extent(raster1), extent(raster2))
    # crop both rasters
    # might be good to check which is bigger and compare
    print("Extents are different, Cropping data")
    raster1<-crop(raster1, overlap)
    raster2<-crop(raster2, overlap)
    # create a stack of the new rasters
  }
    raster.stack<-stack(raster1, raster2)
    return(raster.stack)
}


# check our data
all.data<-stack(HI.data, LiDAR.data)
all.data
# no NAs in this dataframe
```

# Make a df of the indices and examine which are correlated
```{r corr-variables}

# look at correlation bt variables
all.data.df<-as.data.frame(all.data)
cordf<-na.omit(all.data.df)
str(cordf)

# if more than 0.4, correlated, don't use some or put interaction'
coor.cordf<-round(cor(cordf),2)
#export as csv to variables.correlation
write.csv(coor.cordf,"../Outputs/var_cor_no_reflectance.csv")


### ADD REFLECTANCE!!
```

# Load insitu measurements
```{r load_field_measurements}
# Load insitu veg data
# soap_insitu1<-read.csv("../../NEONdata/D17-California/SOAP/2013/insitu/veg-structure/D17_2013_SOAP_vegStr.csv", stringsAsFactors = FALSE)
# we don't need the above because the same info is in the below

soap_insitu<-readOGR("../../NEONdata/D17-California/SOAP/2013/insitu/veg-structure", "soap_stems")
names(soap_insitu)
str(soap_insitu)

# How many species are there at this site?
length(unique(soap_insitu$taxonid))
length(unique(soap_insitu$scientific))

# The data says there are 17 taxonids and 16 spp, so we needed to fix the erroneous taxonid

soap_insitu$taxonid<-gsub("CAIN3", "CEIN3", soap_insitu$taxonid)
# It's fixed! Now there are 16 taxonids and 16 scientific names
```


Sample HI and LiDAR data at stem points and get training and validation data
```{r sample_cube_at_stems}

# Should we sample at 1m pixel or take neighbors? Look at crown diameter stats to decide
soap_insitu<-soap_insitu[-220,] #remove this NA
summary(soap_insitu$maxcanopyd)
# Mean (2.34) and median (1.6) max canopy diameter is over 1m, so sample larger that 1m cell. Create buffers for maxcanopyd/2 for each stem
#The buffer can be specified as a single value, or as a vector of the length of the number of points

buffers<-(soap_insitu$maxcanopyd)/2

# sample buffer specific to mean crown width. The small argument returns a number even if the buffer doesn't include a cell center. Use the mean function so if the buffer includes multiple cells, it will take mean value of those cells.
# sampled_points<-extract(all.data, soap_insitu, buffer=buffers, small=TRUE, fun=mean, na.rm=TRUE)
# Error: Error in apply(x, 2, fun2) : dim(X) must have a positive length

# work-around for the error that happens above
sampled_points1<-extract(all.data, soap_insitu, buffer=buffers, small=TRUE, na.rm=TRUE)
# SP = TRUE, make it spatial, ??extract - one that asks it to return the entire df
# get the mean for each point (buffer) by layer

# The below workaround didn't work:
# sampled_points2<-lapply(sampled_points1, function(x) ifelse(is.matrix(x), colMeans(x), x))
# sampled_points<-do.call(rbind, sampled_points2)

# install.packages("plyr")
library("plyr")

results.df <- as.data.frame(t(sampled_points1[[1]]))
for (i in 2:length(sampled_points1)) {
  if (is.matrix(sampled_points1[[i]])) {
    row.result <- as.data.frame(t(colMeans(sampled_points1[[i]])))
  } else {
    row.result <- as.data.frame(t(sampled_points1[[i]]))
  } 
  results.df <- rbind(results.df, row.result)
}

# combine
sampled_points<-cbind(results.df,soap_insitu$taxonid) 

head(sampled_points)

?extract
### check this out to see if it makes sense. For example, measured tree height vs. sampled tree height and compare w just using global buffer radius

```
?lapply

Function to sample all rasters bc extract doesn't work on rasterstacks
```{r raster_sample_function}
# Function to sample each raster
sample_rasters<-function(rasterlist){
  samples<-extract(raster1, soap_insitu, buffer=buffers, small=TRUE, fun=mean, na.rm=TRUE)
  sampled_points<-do.call(rbind, sampled_points2)
}
  
  breaks_quant<-function(chm){
  breaks<-c(quantile(chm)[2], quantile(chm)[3], quantile(chm)[5])
  return(breaks)
}

sampled_points2<-lapply(sampled_points1, function(x) ifelse(is.matrix(x), colMeans(x, na.rm=TRUE), x))
?do.call
```
?lapply

Random forest classification
```{r random_forest_classification}
# Machine or ensemble learning method. Can do both regression and classification tasks, and undertakes dimensional reduction methods, treats missing values, outlier values and other essential steps of data exploration. It is a type of ensemble learning method, where multiple CART models are combined

# Set a random seed so that results are reproducible next time we load the code - because this process has two sources of randomness (bagging for bootstrap aggregating takes subset of rows and only running subset of samples each time and subset of predictor variables (sqrt of those available))

set.seed(3693)

fit1 <- randomForest(as.factor(Survived) ~ Pclass + Sex + Age + SibSp + Parch + Fare +
                                            Embarked + Title + FamilySize + FamilyID2,
                      data=sampled_points, 
                      importance=TRUE, 
                      ntree=500)
# ntree is number of trees to grow
# 

head(sampled_points)
x <- cbind(x_train,y_train)
# Fitting model
fit <- randomForest(Species ~ ., x,ntree=500)
summary(fit)
#Predict Output 
predicted= predict(fit,x_test)



```

# Fin!


